On-the-fly Algorithms for GKAT Equivalences \thanks{Identify applicable funding agency here. If none, delete this.}

### 2025-01-19 main.tex
remove mention of Z3
update units in table

\begin{table}[H]
\footnotesize
\centering
\setlength{\tabcolsep}{3pt}
\begin{tabular}{l r r r r r}
    Benchmark & DV$_{\textsf{BDD}}$ & TC$_{\textsf{BDD}}$ & DV$_{\textsf{SAT}}$ & TC$_{\textsf{SAT}}$ & SK \\
    \hline
    e250b5p10ne    &   0.19 &   0.18 & 0.20 & 0.23 &    5.82 \\
    e250b5p10eq    &   0.21 &   0.18 & 0.18 & 0.29 &    2.83 \\
    e500b5p50ne    &   0.23 &   0.22 & 0.27 & 0.39 &   37.28 \\
    e500b5p50eq    &   0.26 &   0.21 & 0.28 & 0.57 &   14.06 \\
    e1000b10p100ne &   0.31 &   0.37 & 0.48 & 0.85 & timeout \\
    e1000b10p100eq &   0.37 &   0.28 & 0.44 & 1.04 &   77.83 \\
    e2000b20p200ne &   1.50 &   2.75 & 0.99 & 2.01 & timeout \\
    e2000b20p200eq &   3.34 &   3.03 & 0.67 & 3.14 & timeout \\
    e3000b30p200ne &   1.75 &  26.38 & 1.91 & 4.46 & timeout \\
    e3000b30p200eq &  17.86 &  22.59 & 1.09 & 5.25 & timeout \\
    degenerate     & 220.53 & 232.63 & 0.42 & 0.93 & timeout
\end{tabular}
\caption{Total Time Usage}\label{tab:benchmark-time}
\end{table}

\begin{table}[H]
\footnotesize
\centering
\setlength{\tabcolsep}{3pt}
\begin{tabular}{l r r r r r}
    Benchmark & DV$_{\textsf{BDD}}$ & TC$_{\textsf{BDD}}$ & DV$_{\textsf{SAT}}$ & TC$_{\textsf{SAT}}$ & SK \\
    \hline
    e250b5p10ne    &  15.36 &   14.76 &  6.81 &  7.02 &  114.06 \\
    e250b5p10eq    &  15.56 &   14.95 &  7.06 &  7.25 &  100.48 \\
    e500b5p50ne    &  16.26 &   15.49 &  7.02 &  7.25 &  524.89 \\
    e500b5p50eq    &  17.97 &   15.54 &  7.07 &  7.27 &  546.91 \\
    e1000b10p100ne &  18.36 &   21.41 &  8.22 &  7.99 & timeout \\
    e1000b10p100eq &  20.41 &   17.66 &  8.69 &  7.63 & 5822.66 \\
    e2000b20p200ne & 239.71 &  283.45 & 13.33 & 11.92 & timeout \\
    e2000b20p200eq & 107.92 &  102.46 & 13.20 & 14.02 & timeout \\
    e3000b30p200ne & 112.59 & 1235.46 & 21.44 & 20.10 & timeout \\
    e3000b30p200eq & 245.92 &  228.85 & 21.41 & 18.15 & timeout \\
    degenerate     & 631.47 & 1229.30 & 19.62 & 18.43 & timeout
\end{tabular}
\caption{Peak Memory Usage}\label{tab:benchmark-memory}
\end{table}

@@

GKAT is a guarded fragment of Kleene Algebra with Tests (KAT), which enjoys a symbolic algorithm~\cite{pous_SymbolicAlgorithmsLanguage_2015}.
This algorithm by~\citeauthor{pous_SymbolicAlgorithmsLanguage_2015} generalizes the notion of derivatives also to boolean expressions, which uses binary decision diagram (BDD) as transition between symbolic expressions.
Although some of our examples utilizes BDD to solve equivalence and inequivalence of boolean expressions, because of the structure of GKAT, our algorithm is not bounded by a particular boolean representation or solvers.
In fact, we have demonstrated that in many scenarios, solvers like z3 and sentential decision diagram (SDD) can achieve better performance than BDD.

>>>>

\begin{table}[H]
\footnotesize
\centering
\setlength{\tabcolsep}{3pt}
\begin{tabular}{l r r r r r}
    Benchmark & DV$_{\textsf{BDD}}$ & TC$_{\textsf{BDD}}$ & DV$_{\textsf{SAT}}$ & TC$_{\textsf{SAT}}$ & SK \\
    \hline
    e250b5p10ne    &   0.19 &   0.18 & 0.20 & 0.23 &    5.82 \\
    e250b5p10eq    &   0.21 &   0.18 & 0.18 & 0.29 &    2.83 \\
    e500b5p50ne    &   0.23 &   0.22 & 0.27 & 0.39 &   37.28 \\
    e500b5p50eq    &   0.26 &   0.21 & 0.28 & 0.57 &   14.06 \\
    e1000b10p100ne &   0.31 &   0.37 & 0.48 & 0.85 & timeout \\
    e1000b10p100eq &   0.37 &   0.28 & 0.44 & 1.04 &   77.83 \\
    e2000b20p200ne &   1.50 &   2.75 & 0.99 & 2.01 & timeout \\
    e2000b20p200eq &   3.34 &   3.03 & 0.67 & 3.14 & timeout \\
    e3000b30p200ne &   1.75 &  26.38 & 1.91 & 4.46 & timeout \\
    e3000b30p200eq &  17.86 &  22.59 & 1.09 & 5.25 & timeout \\
    degenerate     & 220.53 & 232.63 & 0.42 & 0.93 & timeout
\end{tabular}
\caption{Total Time Usage (seconds)}\label{tab:benchmark-time}
\end{table}

\begin{table}[H]
\footnotesize
\centering
\setlength{\tabcolsep}{3pt}
\begin{tabular}{l r r r r r}
    Benchmark & DV$_{\textsf{BDD}}$ & TC$_{\textsf{BDD}}$ & DV$_{\textsf{SAT}}$ & TC$_{\textsf{SAT}}$ & SK \\
    \hline
    e250b5p10ne    &  15.36 &   14.76 &  6.81 &  7.02 &  114.06 \\
    e250b5p10eq    &  15.56 &   14.95 &  7.06 &  7.25 &  100.48 \\
    e500b5p50ne    &  16.26 &   15.49 &  7.02 &  7.25 &  524.89 \\
    e500b5p50eq    &  17.97 &   15.54 &  7.07 &  7.27 &  546.91 \\
    e1000b10p100ne &  18.36 &   21.41 &  8.22 &  7.99 & timeout \\
    e1000b10p100eq &  20.41 &   17.66 &  8.69 &  7.63 & 5822.66 \\
    e2000b20p200ne & 239.71 &  283.45 & 13.33 & 11.92 & timeout \\
    e2000b20p200eq & 107.92 &  102.46 & 13.20 & 14.02 & timeout \\
    e3000b30p200ne & 112.59 & 1235.46 & 21.44 & 20.10 & timeout \\
    e3000b30p200eq & 245.92 &  228.85 & 21.41 & 18.15 & timeout \\
    degenerate     & 631.47 & 1229.30 & 19.62 & 18.43 & timeout
\end{tabular}
\caption{Peak Memory Usage (megabytes)}\label{tab:benchmark-memory}
\end{table}

@@

GKAT is a guarded fragment of Kleene Algebra with Tests (KAT), which enjoys a symbolic algorithm~\cite{pous_SymbolicAlgorithmsLanguage_2015}.
This algorithm by~\citeauthor{pous_SymbolicAlgorithmsLanguage_2015} generalizes the notion of derivatives also to boolean expressions, which uses binary decision diagram (BDD) as transition between symbolic expressions.
Although some of our examples utilizes BDD to solve equivalence and inequivalence of boolean expressions, because of the structure of GKAT, our algorithm is not bounded by a particular boolean representation or solvers.
In fact, we have demonstrated that in many scenarios, SAT solvers like MiniSat~\cite{een_MINISAT_2004} can achieve better performance than BDD.
